OceanProteinPlots

### 2024-02-28 Code/OceanProteinPlots.Rmd
Alternate ocean protein plots with NATL2A

PhotosynthLabels <- c("PSII", "Cytb6f", "PSI", "ATP Synthase", "RUBISCO")
ProteinMetabLabels <- c("FtsH1", "FtsH2", "FtsH3", "FtsH4", "Ribosome")
StrainLabels <- c("MED4", "SS120", "MIT9313")

@@

>>>>

PhotosynthLabels <- c("PSII", "Cytb6f", "PSI", "ATP Synthase", "RUBISCO")
ProteinMetabLabels <- c("FtsH1", "FtsH2", "FtsH3", "FtsH4", "Ribosome")
StrainLabels <- c("MED4", "SS120", "MIT9313")
AltStrainLabels <- c("MED4", "SS120", "MIT9313", "NATL2A")

@@

 poi |>
  filter(complex %in% ElectronTrans) |>
  filter(strain %in% AltStrainLabels) |>
  ggplot() +
  geom_point(aes(x = O2, y= depth)) +
  scale_x_continuous(limits = c(0, 260)) +
  scale_y_reverse(limits = c(260, 0)) +
  geom_vline(xintercept = O2_uM,   linewidth = 2, alpha = 0.1) +
  geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.1) +
  facet_grid(factor(strain, levels = c("MED4", "NATL2A", "SS120", "MIT9313")) ~ factor(complex, levels = c("psii", "cytb6f", "psi", "rubisco", "atp"), labels = PhotosynthLabels)) +
  labs(y = "Depth (m)",
       x = expression("O"[2] ~ "(µM)")) +
    # ) +
  theme_bw()

 ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "NATLProchloroPhotosynthDepthO2.png")))
 ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "NATLProchloroPhotosynthDepthO2.tiff")))

poi |>
  filter(complex %in% ProteinMetab) |>
  filter(strain %in% AltStrainLabels) |>
  ggplot() +
  geom_point(aes(x = O2, y= depth)) +
  scale_x_continuous(limits = c(0, 260)) +
  scale_y_reverse(limits = c(260, 0)) +
  geom_vline(xintercept = O2_uM,   linewidth = 2, alpha = 0.1) +
  geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.1) +
  facet_grid(factor(strain, levels = c("MED4", "NATL2A", "SS120", "MIT9313")) ~ factor(complex, levels = c("ftsh1", "ftsh2", "ftsh3", "ftsh4", "ribosome"), labels = ProteinMetabLabels)) +
   labs(y = "Depth (m)",
        x = expression("O"[2] ~ "(µM)")) +
  theme_bw()

 ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "NATLProchloroProteinMetabDepthO2.png")))
 ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "NATLProchloroProteinMetabDepthO2.tiff")))
